Solving a probabilistic planning problem by presenting a history in the field of probabilistic planning

### 2014-04-13 FinalPaper/paper.tex
Improving conclusion

Two types of probabilistic planners are MDP solvers and replanners.
Surprisingly replanners performed extremely well in the first IPPC
competitions, especially FF-Replan in IPPC-04. Later, with FH-MDPs replanners
failed to be scalable and sensitive to an expected reward maximization, the
evaluation criteria for those domains. \textsc{Gourmand} is a state-of-the-art
MDP solver that performed better than other planners like \textsc{Glutton} or
PROST.

@@

Finally we described to other relevant planners RFF and PROST\. RFF is a
planner similar to FF-Replan, but instead works off-line and generates
policies. PROST is a UTC based probabilistic planner that outperformed
\textsc{Gourmand}'s predecessor \textsc{Glutton}.

>>>>

Replanners surprisingly outperformed other planners in the first IPPC domains,
especially FF-Replan in IPPC-04. The good performance for replanners was
because of the way domains were constructed. Later competitions used FH-MDPs.
\textsc{Gourmand} is a state-of-the-art MDP solver that performed better than
other planners like \textsc{Glutton} or PROST for FH-MDP benchmark domains.

@@

As the current planning domain is probabilistically interesting, the
\textsc{Gourmand} planner is favorable. However, by modifying the drone's
communication protocol by adding a handshake protocol any communication failure
can be detected. The UAV can therefore choose to initiate another transmission
of the message until it received an acknowledgment. This way the dead-ends are
replaced with higher costs actions similarly to the \textsc{Navigation} domain.
These higher cost actions are however somewhat more realistic as they do not
mean the disappearance of a highly expensive piece of equipment, but rather a
data package. As this is a realistic and often occurring communicating
protocol, we believe that FF-Replan is in fact a proper alternative for the
current state-of-the-art probabilistic planner.
